Algorithm explanation

### 2013-08-22 article/algo.tex

The construction of the algorithm is in two fold.
\begin{itemize}
\item \textbf{Iterative Constraint Building} The process starts from
  generating the weakest constraint that the graph allows and
  iteratively strengthen a constraint until the strongest one.
\item \textbf{Graph Restructuring} If the constraint become
  unsatisfiable during the iteration, restructure the input Horn graph
  to enlarge the solution template.
\end{itemize}
This algorithm enables a solution to be build as simple as possible.

All vertices with predicate variable labels are assigned a simple
template.  For a vertex with a label $P(\mathbf{x})$, the algorithm
assigns a template $\mathbf{a_P} \mathbf{x} + b_P \leq 0$.  Parameters
$\mathbf{a_P}$ and $b_P$ are specified by a linear constraint.

For each predicate variable vertex, build a linear constraint that
parameters in predicate variable templates must satisfy.  The process
is equivalent to generate a linear constraint in interpolation.

$\genConstr$ procedure produces the constraint for all vertices. The
constraints are first built the weakest so that the disjunctiveness of
whole solution template is fixed first.

>>>>

The construction of the algorithm is in two fold.
\begin{itemize}
\item \textbf{Iterative Constraint Building} The process starts from
  generating the weakest constraint that the input Horn graph allows and
  iteratively strengthen a constraint until the strongest one.
\item \textbf{Graph Restructuring} If the constraint become
  unsatisfiable during the iteration, restructure the input Horn graph
  to enlarge the solution template.
\end{itemize}
This algorithm enables a solution to be build as simple as possible.

For the input graph, each predicate variable vertex has a unique
predicate variable label assigned.  All predicate variables are
assigned a simple template.  For a predicate variable $P(\mathbf{x})$,
the algorithm assigns a template $\mathbf{a}_P \mathbf{x} + b_P \leq
0$.  Parameters $\mathbf{a}_P$ and $b_P$ are specified by a linear
constraint.  Then, according to the graph structure, the algorithm
builds a linear constraint that parameters in predicate variable
templates must satisfy.  For constraint building, the algorithm
traverses the graph in the topological order on $V_\Rightarrow$, and
concatenate the constraints from predecessors to build the problem
constraints. Each process to build a constraint on $\mathcal{HC}_v$
for all vertices $v \in V_\Rightarrow$ is equivalent to generate a
linear constraint in interpolation.

$\genConstr$ procedure produces the constraint for a given vertex $v$.

The constraints are first built the weakest so that the disjunctiveness of
whole solution template is fixed first.
